\documentclass{article}
\usepackage{amsmath,amssymb}
\begin{document}

\section*{Capacity scaling under weak correlations (note)}

This note records a reviewer-facing derivation template for a capacity-style scaling law.
It is not a theorem unless the assumptions are verified for the trained weight regime.

\paragraph{Setup.}
Let $h_i = \sum_j W_{ij} s_j$ be the local field for $s \in [-1,1]^N$.
Assume $\mathbb E[W_{ij}]=0$ and $\mathrm{Var}(W_{ij})=\sigma^2$ for $i \ne j$ and $W_{ii}=0$.

\paragraph{Assumption (weak-correlation approximation).}
The derivation treats the effective off-diagonal weights as approximately independent.
After local learning rules (e.g., Storkey-like updates), weights become correlated; therefore,
any resulting closed-form capacity law must be treated as an asymptotic estimate unless
the field variance scaling is empirically validated.

\paragraph{Variance proxy.}
Under independence, $\mathrm{Var}(h_i) \propto N \sigma^2$.
Introducing a reciprocity parameter $\rho$ via symmetric pairs primarily changes the
symmetry of $W$, i.e. the relative mass of its symmetric part $S=(W+W^\top)/2$
and antisymmetric part $A=(W-W^\top)/2$, rather than changing the per-row variance
of $W$ itself.

\paragraph{Empirical validation.}
We measure (i) $\mathrm{Var}(h_i)$ versus $N$ and (ii) the antisymmetry fraction
$\|A\|_F / \|W\|_F$ and $\mathrm{corr}(W, W^\top)$ versus $\rho$, and verify that the
generated or learned weight regimes satisfy the assumptions used in the estimate.

\end{document}
